The growth of children's semantic and phonological networks: insight from 10 languages

### 2019-02-06 journal/ms.Rmd
second version journal

---
title             : "Noun Learning as Network Growth: A Cross-linguistic Analysis"
shorttitle        : "Noun Learning as Network Growth"
#numbersections: true

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.  In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had semantic associates in the free association norms.

>>>>

---
title             : "The growth of children’s semantic and phonological networks: insight from 10 languages"
shorttitle        : "Lexical Development as Network Growth"
#numbersections: true

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.

### 2019-02-06 journal/ms.tex
second version journal

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Noun Learning as Network Growth: A Cross-linguistic Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Essential manuscript parts
  \title{Noun Learning as Network Growth: A Cross-linguistic Analysis}

  \shorttitle{Noun Learning as Network Growth}

@@

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds, in
comprehension, to the network by 18 months, and in production, to the
network by 30 months). This global network is the end-state towards
which both INT and EXT converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that may a priori hint at an
INT- or EXT-like growth. In order to compare various predictors on the
same data, we restrict the analysis to the subset of nouns for which we
had semantic associates in the free association norms.

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Essential manuscript parts
  \title{The growth of children's semantic and phonological networks: insight
from 10 languages}

  \shorttitle{Lexical Development as Network Growth}

@@

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds, in
comprehension, to the network by 18 months, and in production, to the
network by 30 months). This global network is the end-state towards
which both INT and EXT converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that may a priori hint at an
INT- or EXT-like growth.
